\documentclass[11pt]{article}

\usepackage{latexsym}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{nopageno}
\usepackage{changepage}
\usepackage{fontawesome}
\usepackage[a4paper, top=0.2in, left=0.3in, right=0.4in, bottom=0.2in]{geometry}

% Setup appearance of hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=RoyalBlue,
    urlcolor=RoyalBlue,
}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Changing bullet styles
%-------------------------
% Custom commands
\newcommand{\resumeSubItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-4pt}}
  }
}
% All commands required to define list of job descriptions
\newcommand{\jobDescriptionsListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\jobDescription}[5]{  % Args order [5]: Company name, location, position, time, project description
  \vspace{-5pt}
  \item
    \begin{tabular*}{0.99\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}
    \\*[3pt]
    \begin{adjustwidth}{1pt}{}
    #5\vspace{-7pt}
    \end{adjustwidth}
}

\newcommand{\jobAchievement}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\jobAchievementsListEnd}{\end{itemize}\vspace{-4pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%
\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Anna Zapaishchykova}  
  \\*Baltimore, MA
   & \href{mailto:anna.zapaishchykova@tum.de}{anna.zapaishchykova@tum.de}
 \\
  \href{https://www.linkedin.com/in/anna-zapaishchykova/}{linkedin.com/in/anna-zapaishchykova/} & +49 (159) 0147-10-32\\
  
  
\end{tabular*}
	\vspace{2pt}\\*{\textbf{Languages \& Software:} Python, C\#, Unity, Slicer 3D}

%-----------EDUCATION-----------------
\section{Education}
\begin{itemize}[label={}]
	\vspace{5pt}
	\jobDescription
	{John Hopkins University}{Baltimore, MA}
	{Master thesis}{Mar 2020 - Now}
	{}
	\jobDescription
	{Technical University of Munich}{Munich, Germany}
	{Master of Science in Biomedical Computing}{Sep 2018 - Now}
	{}
	\jobDescription
	{National Technical University of Ukraine "Kyiv Politechnic Institute"}{Kyiv, Ukraine}
	{Bachelor of Science in Computer Engineering}{Sep 2013 - Jun 2017}
	{}
\end{itemize}
%-----------EXPERIENCE-----------------
\vspace{-10pt}
\section{Experience}
  \begin{itemize}[label={}]
  	\vspace{5pt}
  	\jobDescription
  	{Research group MITI, Klinikum rechts der Isar, TUM}{Munich, Germany}
  	{Research assistant}{Jan 2019 - Feb 2020}
  	{Key tools: Keras, Python, Matlab, Docker, Git}
      \begin{itemize}
        \jobAchievement{Worked on phase prediction task in laparascopic surgery and implemented SoA \\*Deep Learning 
        	architectures such as ResNetv2-50 into the operating room.}
        \jobAchievement{Improved data collection in the operating room.}
    \end{itemize}
    \jobDescription
      {CCI-interactive}{Kyiv, Ukraine}
      {Robotic process automation engineer}{Mar 2018 - Sep 2018}
      {Key tools: BluePrism, UIPath}
      \begin{itemize}
        \jobAchievement{Worked as a process automation engineer in one of the biggest banks in Ukraine.}
        \jobAchievement{Certified BluePrism developer.}
    \end{itemize}
    \jobDescription
      {1+1 Media}{Kyiv, Ukraine}
      {Finance Analyst}{Nov 2016 - Mar 2018}
      {Key tools: VBA, MS Excel, MySQL}
      \begin{itemize}
        \jobAchievement{Was responsible for the budget of one of the main TV-channels in Ukraine.}
        \jobAchievement{Successfully created and maintained VBA scripts, reduced amount of routine work.}
    \end{itemize}
    \jobDescription
      {Kodisoft}{Kyiv, Ukraine}
      {Software Developer}{Jan 2015 - Nov 2016}
      {Key tools: C\#, G-codes, CNC-machines programming}
      \begin{itemize}
        \jobAchievement{Created a software for generating machine G-codes.}
        \jobAchievement{Successfully conducted "Internship-2016", interviewed prospective students.}
    \end{itemize}
  \end{itemize}

%-----------Extracurricular Activities-----------------
\section{Extracurricular Activities}
    \subsection*{Hackathons}
      \begin{itemize}
        \resumeSubItem{AIBoost DataScientarium Kyiv 2017 - 1st place}
          {Implemented DL-based online doctor chat with a team of 3 developers in 48 hours.}
        \vspace{-8pt}
      \end{itemize}
    \subsection*{Certifications \& Scholarships}
        \begin{itemize}
        	\resumeSubItem{PROMOS Scholarship 2020}{Awarded for a stay abroad for writing Master thesis.}
        	\resumeSubItem{MedInnovate program graduate 2020}{Learned how to successfully identify unmet clinical needs within the clinical routine, as a result created a VR product for Multiple Sclerosis patients \url{http://www.viz.care}}
            \resumeSubItem{Lviv Data Science Summer School 2017}{Completed intensive 2 week training in Data Science, as a final project worked on "Alzheimer disease conversion prediction".}
        \vspace{-8pt}
        \end{itemize}
    \subsection*{Other}
        \begin{itemize}
            \resumeSubItem{Languages}
              {English(TOEFL-98), Ukrainian(bilingual), Russian(bilingual), German(B2) }
            \resumeSubItem{Interests}{Medical field, neurodegenerative diseases and computer aided procedures}
        \end{itemize}
%-------------------------------------------
\end{document}